The Emperor Has No Clothes

### 2011-04-20 Winds/papers/LBG_Lya/lya_lbg.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5914 ac11df5e-a788-c23b-a8e1-c758c323924d

Second, we have modeled the attenuation of photons near \lya\ by the
IGM surrounding LBGs on scales of $\sim 100\,
{\rm kpc} - 10$\,Mpc.  Our approach follows the method of
\cite{santos04}, using the \cite{barkana04} model for infall onto
galactic halos at $z \approx 3$.  We assume a galaxy with dark matter
halo mass $M_{\rm DM} \approx 10^{12} \msun$, virial radius $\mrvir 
= 80$\,kpc, circular velocity $v_{\rm c} = 220 \mkms$, and an
IGM with $T = 10^4$\,K.  THis amterial is bathed in a uniform
extragalactic UV
background (EUVB) radiation field with ionization rate $\Gamma =
10^{-12.5} \, \rm s^{-1}$ \citep{fpl+08}.  With this parameterization,
we can calculate the density and velocity profiles of gas at $r >
\mrvir$ for the LBG (and assume the gas at $r\le \mrvir$ is dominated by
the outflow) and apply the Sobolev approximation to calculate the
optical depth $\tigm$ to \lya\ as a function of velocity.
We caution that
this $\exp(-\mtigm)$ prescription does not capture the complexity of
gas on these scales.  Indeed, \cite{zheng10a} have argued that a more
proper treatment tends to yield even higher average opacity.
[INCLUDE THE BOOST? Yes, and justify to match $D_A$]
[CHECK against Djisktra]
Therefore, one may wish to consider our estimation of \tigm\ as a
lower limit.

@@

Adopting the minimum value for $\mmc/\sigma$ from above,  we derive the mass,
mass flux, energy, and power profiles shown in
Figure~\ref{fig:mass_energy}.
[Note that the clump flux ($nvr^2$) is nearly constant (increases by a
factor of 2 somehow!) at $10^{-2}$ clumps/yr].
Integrating the mass profile of the clumpy wind, we calculate 
$M_{\rm TOT} \approx 10^{10} \msun$ [check] with nearly all of this
matter laying at radii $r>20$\,kpc.  Ironically, this material accounts for very little
of the down-the-barrel absorption\footnote{The only indisputable
  outflow component.} in the model: XX\%\ of the mass in the flow
corresponds to XX\%\ of the absorption.  
[Can momentum driven winds get this much energy/mass flux?]

@@

\begin{figure}
%\includegraphics[scale=0.6,angle=90]{Figures/mass_energy.ps}
\caption{
Mass, energy
}
\label{fig:mass_energy}
\end{figure}

>>>>

Second, we have modeled the attenuation of photons near \lya\ by the
IGM surrounding LBGs on scales of $\sim 100\,
{\rm kpc} - 10$\,Mpc.  Our approach follows the method of
\cite{santos04}, using the \cite{barkana04} model for infall onto
galactic halos at $z \approx 3$.  We assume a galaxy with dark matter
halo mass $M_{\rm DM} \approx 10^{12} \msun$, virial radius $\mrvir 
= 80$\,kpc, circular velocity $v_{\rm c} = 220 \mkms$, and an
IGM with $T = 10^4$\,K.  THis amterial is bathed in a uniform
extragalactic UV
background (EUVB) radiation field with ionization rate $\Gamma =
10^{-12.5} \, \rm s^{-1}$ \citep{fpl+08}.  With this parameterization,
we can calculate the density and velocity profiles of gas at $r >
\mrvir$ for the LBG (and assume the gas at $r\le \mrvir$ is dominated by
the outflow) and apply the Sobolev approximation to calculate the
optical depth \tigm\ to \lya\ as a function of velocity.
We caution that
this $\exp(-\mtigm)$ prescription does not capture the complexity of
gas on these scales.  Indeed, \cite{zheng10a} have argued that a more
proper treatment tends to yield even higher average opacity.
[INCLUDE THE BOOST? Yes, and justify to match $D_A$]
[CHECK against Djisktra]
Therefore, one may wish to consider our estimation of \tigm\ as a
lower limit.

@@

Adopting the minimum value for $\mmc/\sigma$ from above,  we derive the mass,
mass flux, energy, and power profiles shown in
Figure~\ref{fig:mass_energy}.
[Note that the clump flux ($nvr^2$) is nearly constant (increases by a
factor of 2 somehow!) at $10^{-2}$ clumps/yr].
Integrating the mass profile of the clumpy wind, we calculate 
$M_{\rm TOT} \approx 10^{10} \msun$ [check] with nearly all of this
matter laying at radii $r>20$\,kpc.  Ironically, this material accounts for very little
of the down-the-barrel absorption\footnote{The only indisputable
  outflow component.} in the model: XX\%\ of the mass in the flow
corresponds to XX\%\ of the absorption.  
[Can momentum driven winds get this much energy/mass flux?]
This massive outflow was instead motivated by the significant
absorption toward background sources.

@@

\begin{figure}
\includegraphics[scale=0.6,angle=90]{Figures/fig_lbg_mass_etc.ps}
\caption{
Mass, energy
}
\label{fig:mass_energy}
\end{figure}
